---
title: "Oliver Twist"
author: "Adejumo Ridwan Suleiman"
date: "`r Sys.Date()`"
output: html_document
---

## Project Gutenberg


## libraries 
```{r}
library(tidyverse)
library(dplyr) #data manipulation
library(purrr) #functional programming
library(tidytext) #text mining
library(gutenbergr) #project gutenberg package
library(ggplot2) #data visualization
```

# Load the novel Oliver Twist
```{r}
# Check for book id
gutenberg_metadata %>% 
  filter(title == "Oliver Twist")

# create book data
oliver_twist <- gutenberg_download(730)
```


# Unnest token and stopword removal
- Tokens are sentences broken into words
- Stop words are commonly used words

```{r}
tidy_oliver_twist <- oliver_twist %>% 
  unnest_tokens(word, text) %>% 
  anti_join(stop_words)

tidy_oliver_twist
```

# Word Frequency
```{r}
tidy_oliver_twist %>% 
  count(word, sort = TRUE)
```

# Word Frequency visualization
```{r}
tidy_oliver_twist %>% 
  count(word, sort = TRUE) %>% 
  filter(n > 200) %>%
  top_n(10) %>% 
  ggplot(aes(reorder(word, n),n,fill = word)) +
  geom_col() +
  coord_flip() +
  labs(y = NULL, x = "word", title = "The Most Common Words in Oliver Twist")
```

# Sentiment Analysis(using bing)
- This is the analysing of the sentiment of a particular text 
- We have 3 general purpose lexicons that classify words into various sentiment
  * AFINN - uses a numerical range of -5 t0 +5 with negative scores indicating negative sentiment and positive scores indicating positive sentiment.
  * bing - classifies words into positive and negative
  * nrc - classifies into positive, negative, anger, anticipation, disgust, fear, joy, sadness, surprise and trust.
  
- Bing categorizes words into negative and positive categories
```{r}
bing_word_counts <- tidy_oliver_twist %>%
  inner_join(get_sentiments("bing")) %>%
  count(word, sentiment, sort = TRUE) 

bing_word_counts
```

# Most common postive and negative words
```{r}
bing_word_counts %>%
  group_by(sentiment) %>% 
  slice_max(n, n = 10) %>% 
  ungroup() %>% 
  ggplot(aes(x = n, y = reorder(word, n), fill = sentiment)) +
  geom_col(show.legend = FALSE) +
  facet_wrap(~sentiment, scales = "free_y") +
  labs(x = "Contribution to sentiment",
       y = NULL)
```

# Word Cloud (most common negative and positive words)
In other functions, such as wordcloud::comparison.cloud(), you may need to turn the data frame into a matrix with reshape2’s acast().
```{r}
library(wordcloud)

bing_word_counts %>%
  reshape2::acast(word ~ sentiment, value.var = "n", fill = 0) %>%
  comparison.cloud(colors = c("red", "blue"),
                   max.words = 50)
```

